\plaintitle

### 2016-09-05 drafts/labor/cases.tex
complexity and some slicing stuff

\subfile{complexity}
\subfile{slicing}

%   __ _           _ _     _ _ _ _         
%  / _| | _____  _(_) |__ (_) (_) |_ _   _ 
% | |_| |/ _ \ \/ / | '_ \| | | | __| | | |
% |  _| |  __/>  <| | |_) | | | | |_| |_| |
% |_| |_|\___/_/\_\_|_.__/|_|_|_|\__|\__, |
%                                    |___/

% how much volatility and quality can we deal with?
% how to measure, get rid of people, recover from bad workers
%mason's on getting workers to be better
\subsubsection{Volatile quality and availability? How much can you deal with?}\label{sec:flexibility}
A number of researchers have identified
worker attrition,
variability of worker performance,
and uncertainty about good versus bad--faith actors as open questions of crowdwork
\cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
\ali{We can and should discuss the distinction between presumably ``bad faith'' workers
\& workers who are merely responding in kind to bad requesters
--- and the broader questions surrounding
the roles that requesters as well as workers should play ---
but let it suffice to say that
requesters have been trying to understand and manage what appears to them as inconsistent work.
Their ways of responding to that variance in work quality has largely involved
making the work more flexible and resilient to work
(although some work has gone into investigating the causes, rather than treating the symptoms)}

Earlier we discussed \citeauthor{cheng2015break}'s work
measuring the impact that interruption has on worker performance
\cite{cheng2015break}.
This work illustrates a broader sentiment in
both the study and practice
of crowdwork, that microtasks should be designed resiliently against the variability of workers,
fully exploiting the abstracted nature of each piece of work
\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
That is to say, micro--tasks should be designed such that a single worker's poor performance,
or a good worker's sudden departure,
does not significantly impact the agenda of the work as a whole.
While \citeauthor{cheng2015break} found costs with breaking tasks into smaller components
in the form of higher cumulative time to complete
(albeit much shorter real time to complete, owing to parallelization),
\citeauthor{delayAndOrderLasecki} found that at least \textit{some} performance can be recouped by stringing 
similar tasks together
\cite[respectively]{cheng2015break,delayAndOrderLasecki}.

\citeauthor{embracingErrorKrishna} take a different approach;
by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
the authors offer orders--of--magnitude improvements
in various binary classification tasks
\cite{embracingErrorKrishna}.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of it instead:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

The work thus far seems to attempt to maximize the quality of work among workers through various means:
\begin{inlinelist}
  \item Identifying ``bad'' workers (fraught with problems as this characterization is) \cite{MaliciousCrowdworkersGadiraju},
  \item Designing tasks with break points to facilitate the on--boarding and off--boarding that happens anyway \cite{cheng2015break}, and
  \item Expecting certain levels of attrition and incorrectness and using that variability to their advantage \cite{embracingErrorKrishna}
\end{inlinelist}.

Flexibility has been explored through the lens of Fordism, perhaps best illustrated by
\citeauthor{tolliday1986between}'s treatment describing
turnover rates rising above 300\% in the decade leading to the introduction of the assembly line in 1913.
Specifically, the utilization of ``\dots~`semi--special' machine tools which could be adapted
[and]~\dots~added flexibility through seasonal layoffs for production workers and the use of
piece rates~\dots~rather than a day wage system''
\cite{tolliday1986between}.

In the field of piecework,
the research covering this topic has both explored
a breadth of tasks that might be rendered doable by piecemeal workers
\textit{as well as} longitudinally documented the success of these approaches.
Here, we

Here, \citeauthor{hu1961parallel}'s work,
saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',
parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,
and indeed the study of factory and mass manufacturing labor through the \nth{20} century,
substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,
and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

% what can be decomposed? what can be evaluated?
% technology/turuing completeness gets us a win
% predefined expertise? you can find someone almost instantly;
% ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% huddler paper cites some decomposition stuff workflows are good/bad at things
% 3-way slack w/msb and mav
% academy of management 
% van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
\section{Graveyard}

\endnotetext{
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
}

\subsection{What forms of work design and worker management are viable?}
\begin{itemize}
  \item researchers have looked at how to increase worker productivity
  (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
  \cite{measuringCrowdsourcingCheng}.
  \item we've also seen people ``embrace error''
  \cite{embracingErrorKrishna}.
  \item still other research has looked into ways to sandbox workers from the context of their work 
  \item but scholarship looking into the design and management of work and workers isn't new;
  lots of research into getting pieceworkers to do work more quickly
  \cite{seymour1954manual}.
  \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
  (echoing similar research on Wikipedia and Mechanical Turk)
  \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
\end{itemize}

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.

  \theendnotes
  \end{appendices}
  }

>>>>

\subfile{complexity}
\subfile{slicing}
\subfile{flexibility}

\endnotetext{
Here, \citeauthor{hu1961parallel}'s work,
saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',
parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,
and indeed the study of factory and mass manufacturing labor through the \nth{20} century,
substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,
and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

% what can be decomposed? what can be evaluated?
% technology/turuing completeness gets us a win
% predefined expertise? you can find someone almost instantly;
% ease of doing this makes it qualitatively different due to Channel Factors (diverting a channel/river)
% huddler paper cites some decomposition stuff workflows are good/bad at things
% 3-way slack w/msb and mav
% academy of management 
% van der ven paper ~1972 limits of workflows cited in daniela's flash orgs paper
}

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
% \section{Graveyard}

\endnotetext{
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
}
\endnotetext{
\subsection{What forms of work design and worker management are viable?}
\begin{itemize}
  \item researchers have looked at how to increase worker productivity
  (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
  \cite{measuringCrowdsourcingCheng}.
  \item we've also seen people ``embrace error''
  \cite{embracingErrorKrishna}.
  \item still other research has looked into ways to sandbox workers from the context of their work 
  \item but scholarship looking into the design and management of work and workers isn't new;
  lots of research into getting pieceworkers to do work more quickly
  \cite{seymour1954manual}.
  \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
  (echoing similar research on Wikipedia and Mechanical Turk)
  \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
\end{itemize}

@@

    Resistance against managers in piecework and factory labor settings are deeply well--explored,
    but perhaps the most relevant case study to draw on here is to be found in
    \citeauthor{waldinger1996helots}'s case study of ``Justice for Janitors'',
    where marginalized workers managed to raise awareness for their plight and secure support for badly needed reforms
    \cite{waldinger1996helots}.
    The achievements of labor advocacy groups such as labor unions as resistant,
    even adversarial organizations counter--balancing the management
    is somewhat well--understood
    \cite{russell1982collective,craig1992behavior}.
    We argue that these threads of resistance against management in various forms
    are in fact one.
}
  \theendnotes
  \end{appendices}
  }

### 2016-09-05 drafts/labor/complexity.tex
complexity and some slicing stuff

\subsubsection{Achieving greater complexity
\joke{ --- or ``making crowd--work \textit{yuge}''}
% i think it says a lot about my confidence in my latex skillz that i'm willing to put these in the subfile
}\label{sec:Complexity}
% crowd weaver, aditya and someone else's book
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task'',
argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

@@

\topic{Digital media have expanded the scope of viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity.
Given the flourishing of on--demand labor platforms such as
Uber, Amazon Mechanical Turk, and others, we ask ourselves
what --- if anything --- has changed.
We argue that the Internet has trivialized the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code}
\end{inlinelist}.

\topic{\joke{great} topic sentence here.}
% \topic{While much of the above work has focused on
% clever arrangements of systems to manage collectives of workers,
% another body of work has turned inward toward managing the self.}
\citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
(of sorts)
will prove relevant as we trace the literature surrounding piecework.

\endnotetext{
  This is also kind of off-topic, isn't it? where to take it?

  \topic{A smaller but growing body of work has reflected on this
  and brought to our attention a number of ethical questions surrounding the
  increasing complexity of crowdwork and the hazards that increasingly arise.}
  \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
  --- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
  for instance ---
  but these and other dangers range an enormous landscape % too informal?
  \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

  kill this?

@@

\citeauthor{10.2307/23702539} also argues that
a significant obstacle to the introduction of piecework in railroad shops was
the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely
if ever
interact face--to--face and
opportunities for coordination and collective action are severely limited,
we should expect to see
the challenges stymieing collective action
that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
  \clearpage
  \nobalance{}
  \begin{appendices}
  \theendnotes
  \end{appendices}
}

>>>>

\subsubsection[finding crowdwork's limits]{Achieving greater complexity
\joke{ --- or ``making crowd--work \textit{yuge}''}
}\label{sec:Complexity}
% crowd weaver, aditya's book

\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

@@

\subsubsubsection{\pieceworkpers}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task'',
argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

@@

\subsubsubsection{\whatchanged}
\topic{Digital media have expanded the scope of
viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity.
Given the flourishing of on--demand labor platforms such as
Uber, Amazon Mechanical Turk, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the Internet has trivialized
the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of
        ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code}
\end{inlinelist}.

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties'',
informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

\topic{Technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers,
generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625,
      skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}.

\topic{Crowdsourcing falters when the routinization of complex work proves difficult.}
\ali{Something about complexity being difficult to make routine when
there are lots of little tasks a la \citeauthor{Brown01041990}}

\onlyinsubfile{
  \balance{}
  \printbibliography

  \clearpage
  \nobalance{}
  \begin{appendices}
  \section{Paragraph graveyard}
    \topic{\joke{great} topic sentence here.}
    \citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
    exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
    \cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
    While some of this work doesn't strictly fall under ``crowdsourcing'',
    the [scientific] management of the self as a worker
    (of sorts)
    will prove relevant as we trace the literature surrounding piecework.

    This is also kind of off-topic, isn't it? where to take it?

    \topic{A smaller but growing body of work has reflected on this
    and brought to our attention a number of ethical questions surrounding the
    increasing complexity of crowdwork and the hazards that increasingly arise.}
    \citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
    --- working for increasing amounts of time on tasks of growing complexity,
    only to discover that requesters are not willing to pay,
    for instance ---
    but these and other dangers range an enormous landscape
    \cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

@@

  \citeauthor{10.2307/23702539} also argues that
  a significant obstacle to the introduction of piecework in railroad shops was
  the resistance of workers
  (the other being the resistance of management (for different and varying reasons)).
  In the cases of online platforms like AMT and digitally mediated platforms like Uber,
  where in both cases workers rarely
  if ever
  interact face--to--face and
  opportunities for coordination and collective action are severely limited,
  we should expect to see
  the challenges stymieing collective action
  that we see in \citeauthor{dynamo} and elsewhere
  \cite{10.2307/23702539,dynamo}.
  \end{appendices}

@@

### 2016-09-05 drafts/labor/flexibility.tex
complexity and some slicing stuff

\subsubsection{Volatile quality and availability? How much can you deal with?}\label{sec:flexibility}
A number of researchers have identified
worker attrition,
variability of worker performance,
and uncertainty about good versus bad--faith actors as open questions of crowdwork
\cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
\ali{We can and should discuss the distinction between presumably ``bad faith'' workers
\& workers who are merely responding in kind to bad requesters
--- and the broader questions surrounding
the roles that requesters as well as workers should play ---
but let it suffice to say that
requesters have been trying to understand and manage what appears to them as inconsistent work.
Their ways of responding to that variance in work quality has largely involved
making the work more flexible and resilient to work
(although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

\onlyinsubfile{
  % \balance{}
  \printbibliography
}

>>>>

\subsubsection[worker volatility]{Volatile quality and availability? How much can you deal with?}
\label{sec:flexibility}

\ali{TODO:
\begin{enumerate}
  \item segue
  \item \crowdworkpers
  \item \pieceworkpers
  \item \whatchanged
\end{enumerate}
}

A number of researchers have identified
worker attrition,
variability of worker performance,
and uncertainty about good versus bad--faith actors as open questions of crowdwork
\cite{MaliciousCrowdworkersGadiraju,Ipeirotis:2010:QMA:1837885.1837906}.
\ali{We can and should discuss the distinction between presumably ``bad faith'' workers
\& workers who are merely responding in kind to bad requesters
--- and the broader questions surrounding
the roles that requesters as well as workers should play ---
but let it suffice to say that
requesters have been trying to understand and manage what appears to them as inconsistent work.
Their ways of responding to that variance in work quality has largely involved
making the work more flexible and resilient to work
(although some work has gone into investigating the causes, rather than treating the symptoms)}

@@

\onlyinsubfile{
  % \balance{}
  % \printbibliography
}

### 2016-09-05 drafts/labor/slicing.tex
complexity and some slicing stuff

\subsubsection{Slicing work smaller
\joke{ --- or ``putting the {\tiny `micro'} in microwork''}
}\label{sec:Slicing}

@@

\subsubsubsection{Crowdwork's perspective.}
\topic{The research on crowdwork and decomposition has generally driven toward finding new ways
to strip unnecessary context from work,
allowing tasks to be broken down into smaller parts.}
As \citeauthor{verroios2014context} frame it,
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
% the decomposition of work allows requesters to assign tasks to workers in parallel,
% theoretically scaling to as many workers as there are tasks.
% As the nature of the work has grown in complexity,
% so too has the challenge of parallelizing and decontextualizing work;
Researchers have thus investigated the role of
distributed, contextually independent work
in the contexts of collaborative writing of various forms,
software development,
classification, and myriad other purposes
\cite{Kittur:2009:CCI:1518701.1518928,Baecker:1993:UID:169059.169312,
      10.2307/1562247,karnin2010crowdsourcing,bragg2013crowdsourcing,
      chilton2013cascade}.

% \topic{i was going to say something here about breaking work apart to the point that nobody can piece things together,
% but i think this would be more interesting as a commentary on trusting workers or something.}
% Given that much of the focus in crowdsourcing has focused on information work,
% \citeauthor{sensitiveTasks}, for instance,
% illustrate one approach to ensuring that workers never become aware of
% enough information to piece together sensitive data
% \cite{sensitiveTasks}.

@@

{
\subsubsubsection{Piecework's perspective.}
My goal for this section is to make this all about the assembly line and
scientific management, and how piecework literature tried to measure everything,
but found it untenable given the extra equipment that was necessary
(but generally which didn't exist) to track every movement and action that workers took.

\subsubsubsection{What's changed.}
The finding here is that
crowdwork can be more carefully micro--managed than piecework could be,
and that this is a double--edged sword:
we can effectively give feedback to workers on everything they do,
but this is emboldening us to try to
over--manage workers just as piecework tried to do.}

% The question, then, becomes about how to break tasks down as much as possible
% (as discussed in the previous section)
% without losing the necessary context to do a task.
% ow can we design work so that as little context as possible is provided,
% without leaving out context or information necessary to complete the task?

% While some research has attempted to increase workers' awareness of the work they do in
% apparent efforts to yield higher quality work,
% others have turned this constraint of crowdwork into a feature ---
% the abstraction from the work itself
% appears to allow requesters to engage workers in work with ---
% for instance ---
% sensitive, confidential or otherwise personally identifying information.
% We will discuss these and other avenues of research here.

% \textit{Cascade} demonstrated that it's possible to
% break certain classes of tasks apart
% in such a way that they yield taxonomies of various subjects,
% a task generally thought to be sufficiently complex that only expert workers
% with top--down awareness of the task
% --- in this case, with awareness of all the constituent colors ---
% could complete the task
% \cite{chilton2013cascade}.
% \citeauthor{verroios2014context} further illustrate this potential by
% forming a task one might consider highly contextually dependent
% --- summarizing the contents of a movie ---
% in such a way that crowd workers could contribute small pieces of work without
% needing to know the content of the rest of the project
% \cite{verroios2014context}.

\onlyinsubfile{
  % \balance{}
  \printbibliography
}

>>>>

\subsubsection[slicing work into smaller parts]{Slicing work smaller
\joke{ --- or ``putting the {\tiny `micro'} in microwork''}
}\label{sec:Slicing}

@@

\subsubsubsection{\crowdworkpers}
\topic{The research on crowdwork and decomposition has generally driven toward finding new ways
to strip unnecessary context from work,
allowing tasks to be broken down into smaller parts.}
As \citeauthor{verroios2014context} frame it,
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
Researchers have thus investigated the role of
distributed, contextually independent work
in the contexts of collaborative writing of various forms,
software development,
classification, and myriad other purposes
\cite{Kittur:2009:CCI:1518701.1518928,Baecker:1993:UID:169059.169312,
      10.2307/1562247,karnin2010crowdsourcing,bragg2013crowdsourcing,
      chilton2013cascade}.

@@

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item each task was quickly verifiable by a qualified [human] computer,
  \item tasks were discrete --- independent from one another, and
  \item knowledge of the full scope of the project --- indeed, knowledge of anything more than the problem set at hand ---
  was wholly unnecessary.
\end{enumerate}

\subsubsubsection{\whatchanged}
\ali{todo}

\onlyinsubfile{
  \balance{}
  \printbibliography

  \clearpage
  \nobalance{}
  \begin{appendices}
    \section{Paragraph graveyard}
    The finding here is that
    crowdwork can be more carefully micro--managed than piecework could be,
    and that this is a double--edged sword:
    we can effectively give feedback to workers on everything they do,
    but this is emboldening us to try to
    over--manage workers just as piecework tried to do.

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management,
            and how piecework literature tried to measure everything,
            but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}
  \end{appendices}
}
